%\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[letterpaper]{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{graphicx}
\usepackage{color}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{pdflscape}
\usepackage[hyphens]{url}
\usepackage[colorlinks]{hyperref}
\usepackage{enumerate}
\usepackage{ifthen}
\usepackage{float}
\usepackage{array}
\usepackage{tikz}
\usepackage{multirow} 
\usetikzlibrary{shapes}
\usepackage{algorithm2e}
\usepackage{listings}
%%%% HW instructions / collaboration text

\newcommand{\HWPoliciesmix}{
\paragraph*{Instructions.} {\bf This homework contains two parts. Part A is written assignment and Part B is MATLAB programming assignment.}
}

\newcommand{\HWPolicies}{
\paragraph*{Instructions.} 
Please write up your responses to the following problems clearly and
concisely. We encourage you to write up your responses using \LaTeX{};
we have provided a \LaTeX{} template, available on Canvas, to
make this easier. {\bf Submit your answers in PDF form to Canvas. We will not accept paper copies of the homework.}

\paragraph*{Collaboration.} 
You are allowed and encouraged to work together. You may discuss the
homework to understand the problem and reach a solution in groups up
to size {\bf four students.} However, {\em each student must write
  down the solution independently, and without referring to written
  notes from the joint session. {\bf In addition, each student must
    write on the problem set the names of the people with whom you
    collaborated.}} You must understand the solution well enough in
order to reconstruct it by yourself. (This is for your own benefit:
you have to take the exams alone.)
}
\newcommand{\ProgrammingPolicies}[1]{
\paragraph*{Instructions.} 
This is a MATLAB programming assignment. This assignment consists of
multiple parts. Portions of each part will be graded automatically,
and you can submit your code to be automatically checked for
correctness to receive feedback ahead of time.

We are providing you with codebase / templates / dataset that you will
require for this assignment. Download the file {\tt hw#1\_kit.zip}
from Canvas {\bf before} beginning the assignment.  {\bf Please
  read through the documentation provided in ALL Matlab files before
  starting the assignment.} The instructions for submitting your
homeworks and receiving automatic feedback are online on the wiki:

\begin{center}
\url{http://alliance.seas.upenn.edu/~cis520/wiki/index.php?n=Resources.HomeworkSubmission}
\end{center}

\paragraph*{Collaboration.} 
For this programming assignment, you are allowed to work in pairs, but no more than 2. Each group
is required to submit {\bf ONCE} only. {\bf The LOWEST grade will be recorded for multiple submissions.}
Be sure to include your pennkeys and names in the {\it Group.txt} file.
Failure to do so will result in a failure in the grading process. 
{\bf We will be using automatic checking software to detect blatant copying of other student's assignments, so,
please, don't do it.}
}

%%%% CUSTOM COMMANDS FOR FORMATTING EXAMS/HOMEWORKS
\newcounter{section_points}[section]
\newcounter{header_points}[section]
\newcounter{total_points}

\newcommand{\hpoints}[1]{
  \setcounter{header_points}{#1}
  \textbf{[#1 points]}
}

\newcommand{\points}[1]{
  \addtocounter{section_points}{#1}
  \addtocounter{total_points}{#1}
  \textbf{[#1 
    \ifthenelse{\equal{#1}{1}}
    {point}{points}]}
}

\newcommand{\bpoints}[1]{
  \textbf{[#1 
    \ifthenelse{\equal{#1}{1}}
    {point}{points}]}
}


\newcommand{\point}{\textbf{[1 point]}}

\newboolean{ShowSolutions}
\newcommand{\Mistake}[2]{
  \ifthenelse{\boolean{ShowSolutions}}
  {\paragraph{\bf $\blacksquare$ COMMON MISTAKE #1:} {\sf #2} \bigskip}
  {}
}

\newcommand{\Solution}[2]{
  \ifthenelse{\boolean{ShowSolutions}}
    {
      \paragraph{\bf $\bigstar $ SOLUTION:} { \sf
        #1} \bigskip
    }
    { 
      #2
    } %} \vspace{1.5in}}
}
\newcommand{\out}[1]{}

\newboolean{ShowPointsInfo}

\newcommand{\PointStats}[0]{
  \ifthenelse{\boolean{ShowPointsInfo}}
  {
    \begin{center}

      \begin{tabular}{rl}
        \hline
        Stated Points: & \arabic{header_points} \\
        Section Points: & \arabic{section_points} \\
        Total Points So Far: & \arabic{total_points} \\
        \hline 
        \multicolumn{2}{c}{
          
          \ifthenelse{
            \equal{\value{section_points}}{\value{header_points}}
          }{CORRECT TOTAL}
          {{\bf INCORRECT TOTAL}}
          }
          \\
        \hline
      \end{tabular}
    \end{center}
  }{}
}

\newcounter{blankcount}
\newcommand{\myrepeat}[2] {
\setcounter{blankcount}{1}
\whiledo{\value{blankcount} < #1}{
#2
\addtocounter{blankcount}{1}
}
}

\newcommand{\blank}[1]{\underline{\myrepeat{#1}{\qquad}}}


%%%% CUSTOM MATH GOES HERE

\newcommand{\ind}[1]{\mathbf{1}\left(#1\right)}
\renewcommand{\Pr}{\mathbf{Pr}\xspace}
\newcommand{\Bern}{\textsf{Bernoulli}\xspace}
\newcommand{\sign}{\textsf{sign}}

\newcommand{\E}{\mathbf{E}}
\newcommand{\bx}{\mathbf{x}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\bz}{\mathbf{z}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bl}{\mathbf{\ell}}
\newcommand{\vc}[1]{\mathbf{#1}}

\newcommand{\Hypo}{\mathcal{H}}
\newcommand{\XX}{\mathcal{X}}
\newcommand{\cD}{\mathcal{D}}

\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}

\newcolumntype{M}{>{$\vcenter\bgroup\hbox\bgroup}c<{\egroup\egroup$}}

\newcolumntype{x}[1]{>{\centering\arraybackslash}m{#1}}




